Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Little explanation of the EvoDrawings app

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation 
\cite{picbreeder}.
In order to do this, data about individuals 
must be permanently stored, even
if they are no longer in the active population.

@@

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known were presented to users
along with a ranking of users by their weight was shown in a window, as an example
a screen capture of this interface is shown in figure \ref{fig:top-users}.

>>>>

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

@@

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation.  
\cite{picbreeder}.
In order to do this, data about individuals 
must be permanently stored, even
if they are no longer in the active population.

@@

\subsection{EvoDrawings}
\label{sec:evo_drawings}
The particular application implemented for this work is called
EvoDrawings. In this IEA individuals are drawing created by an animation of three types of 
shapes: equilateral triangles, squares and cirlcles, varying in size and color. The movement of
each shape is defined by a behaviour rule, for instance  ``move straight'', 
``change direction in case of colission'',  etc., this animations are inspired in 
the Process Compendium by Reas \cite{reas2004}, where visual forms 
emerge by the relations of multiple forms and their behavior.

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight. Still the graph is used internally to explore
the social network and the evolution of the population.
\item Non Graph Gamification (G). Only experience is considered for the reputation of users. 
\item Graph Gamification (GG). Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known were presented to users
along with a ranking of users by their weight was shown in a window, as an example
a screen capture of this interface is shown in figure \ref{fig:top-users}.
